---
title: "data-preprocessing"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# Clear workspacce and set default color

```{r reset, include=FALSE}
graphics.off()
rm(list=ls(all.names=TRUE))
options(digits = 3)
```

# Import functions and packages

```{r}

# Install and load required packages
packages = c(
  # CRAN packages
  "tidyverse",
  # Github packages for specialized functions
  "chenyu-psy/smartr@v0.3.2"
)
process_packages(packages, quietly = TRUE)

```


# Experiment 1a

The data has been saved in local folder `./raw_data/Data_Exp1/`

```{r}
Metadata_Exp1.1 <- read_metaData("./raw_data/Data_Exp1.1/metadata.json")
Metadata_Exp1.2 <- read_metaData("./raw_data/Data_Exp1.2/metadata.json")


Metadata_Exp1 <- bind_rows(Metadata_Exp1.1, Metadata_Exp1.2) %>% 
  smartr::extract_data_info(info="participant")


Metadata_Exp1_filtered <- Metadata_Exp1 %>% 
  filter(studyState == "FINISHED" | resultId %in% c(42167, 42185))

Raw_Exp1 <- read_json_data(Metadata_Exp1_filtered$file) %>% 
  group_by(participant) %>% 
  mutate(participant = cur_group_id()) %>% 
  ungroup()

Data_Exp1 <- Raw_Exp1 %>%
  filter(blockID > 0, screenID %in% c("memory-resp", "retrieval")) %>% 
  select(participant, blockID, trialID, condition, screenID, 
         leftColor, rightColor, leftImage, rightImage, correctObject,
         response, acc, rt) %>% 
  mutate(response = as.character(response))
  
Data_Exp1 %>% write_csv(file = "./data/source/Data_Exp1.csv")


Survey_Exp1 <- Raw_Exp1 %>% 
  filter(screenID == "survey") %>% 
  select(participant, response) %>% 
  unnest_wider(response) %>% 
  select(!starts_with("P0"))

Survey_Exp1 %>%
  write_csv(file = "./data/source/Survey_Exp1.csv")


```

# Experiment 1b


```{r}

Metadata_Exp1b <- read_metaData("./raw_data/Data_Exp1b/metadata.json")

Metadata_Exp1b_filtered <- Metadata_Exp1b %>% 
  filter(studyState == "FINISHED") %>% 
  slice(1:50)

Raw_Exp1b <- read_json_data(Metadata_Exp1b_filtered$file) %>% 
  group_by(participant) %>% 
  mutate(participant = cur_group_id()) %>% 
  ungroup()

Data_Exp1b <- Raw_Exp1b %>%
  filter(blockID > 0, screenID %in% c("processing", "memory-resp", "retrieval")) %>% 
  select(participant, blockID, trialID, condition, screenID, 
         leftColor, rightColor, leftImage, rightImage, correctObject, correctJudge,
         response, acc, rt) %>% 
  rename(correctResp=correctJudge) %>% 
  mutate(
    correctResp = case_when(
      condition=="B" & leftImage=="image26" ~ "left",
      condition=="B" & rightImage=="image26" ~ "right",
      TRUE ~ correctResp),
    acc = case_when(
      condition=="B"&screenID=="processing" ~ correctResp==response,
      TRUE ~ acc
    )) %>% 
  mutate(response = as.character(response)) %>% 
  mutate(
    target = case_when(
      screenID=="memory-resp" & leftColor=="#FFFFFF" ~ rightImage,
      screenID=="memory-resp" & rightColor=="#FFFFFF" ~ leftImage,
      screenID=="retrieval" ~ correctObject,
      TRUE ~ NA_character_
    ),
    distractor = case_when(
      screenID=="memory-resp" & correctResp=="left" ~ leftImage,
      screenID=="memory-resp" & correctResp=="right" ~ rightImage,
      TRUE ~ NA_character_
    )
  ) %>% 
  mutate(
    distractor = case_when(
      screenID=="retrieval" ~ distractor[target==target][1],
      TRUE ~ distractor
    ),
    .by = c(participant, blockID, trialID)
  )

Data_Exp1b %>% write_csv(file = "./data/source/Data_Exp1b.csv")

Survey_Exp1b <- Raw_Exp1b %>% 
  filter(screenID == "survey") %>% 
  select(participant, response) %>% 
  unnest_wider(response) %>% 
  select(!starts_with("P0"))

Survey_Exp1b %>%
  write_csv(file = "./data/source/Survey_Exp1b.csv")

```

# Experiment 2a

## Download data
```{r}
# Download the data from JATOS
Metadata_Exp2a <- get_JATOS_data(
  token = "jap_bQ7jROzehBh7WTt0I2CrjLJyBZIUIfkd5079d",
  url = "https://coglab.xyz/jatos/api/v1/results",
  batchId = c(1411),
  dataPath = "./raw_data/Data_Exp2a/"
)

```

## Retrieve data
```{r}

Metadata_Exp2a <- read_metaData("./raw_data/Data_Exp2a/metadata.json") %>% 
  extract_data_info("participant")

Metadata_Exp2a_filtered <- Metadata_Exp2a %>% 
  filter(studyState == "FINISHED")

Raw_Exp2a <- read_json_data(Metadata_Exp2a_filtered$file) %>% 
  group_by(participant) %>% 
  mutate(participant = cur_group_id()) %>% 
  ungroup()

Data_Exp2a <- Raw_Exp2a %>%
  filter(blockID > 0, screenID %in% c("processing", "memory-resp", "retrieval")) %>% 
  select(participant, blockID, trialID, condition, screenID, 
         leftColor, rightColor, leftImage, rightImage, correctObject, correctJudge,
         response, acc, rt) %>% 
  rename(correctResp=correctJudge) %>% 
  mutate(
    # correctResp = case_when(
    #   condition=="B" & leftImage=="image26" ~ "left",
    #   condition=="B" & rightImage=="image26" ~ "right",
    #   TRUE ~ correctResp),
    # acc = case_when(
    #   condition=="B"&screenID=="processing" ~ correctResp==response,
    #   TRUE ~ acc
    # )
    ) %>% 
  mutate(response = as.character(response)) %>% 
  mutate(
    target = case_when(
      screenID=="memory-resp" & leftColor=="#FFFFFF" ~ rightImage,
      screenID=="memory-resp" & rightColor=="#FFFFFF" ~ leftImage,
      screenID=="retrieval" ~ correctObject,
      TRUE ~ NA_character_
    ),
    distractor = case_when(
      screenID=="memory-resp" & correctResp=="left" ~ leftImage,
      screenID=="memory-resp" & correctResp=="right" ~ rightImage,
      TRUE ~ NA_character_
    )
  ) %>% 
  mutate(
    distractor = case_when(
      screenID=="retrieval" ~ distractor[target==target][1],
      TRUE ~ distractor
    ),
    .by = c(participant, blockID, trialID)
  )

Data_Exp2a %>% write_csv(file = "./data/source/Data_Exp2a.csv")

Survey_Exp2a <- Raw_Exp2a %>% 
  filter(screenID == "survey") %>% 
  select(participant, response) %>% 
  unnest_wider(response) %>% 
  select(!starts_with("P0"))

Survey_Exp2a %>%
  write_csv(file = "./data/source/Survey_Exp2a.csv")

```


# Experiment 2b

## Download data
```{r}
# Download the data from JATOS
Metadata_Exp2b <- get_JATOS_data(
  token = "jap_bQ7jROzehBh7WTt0I2CrjLJyBZIUIfkd5079d",
  url = "https://coglab.xyz/jatos/api/v1/results",
  batchId = c(1510),
  dataPath = "./raw_data/Data_Exp2b/"
)

```

## Retrieve data
```{r}

Metadata_Exp2b <- read_metaData("./raw_data/Data_Exp2b/metadata.json") %>% 
  extract_data_info("participant")

Metadata_Exp2b_filtered <- Metadata_Exp2b %>% 
  filter(studyState == "FINISHED")

Raw_Exp2b <- read_json_data(Metadata_Exp2b_filtered$file) %>% 
  group_by(participant) %>% 
  mutate(participant = cur_group_id()) %>% 
  ungroup()

Data_Exp2b <- Raw_Exp2b %>%
  filter(blockID > 0, screenID %in% c("processing", "memory-resp", "retrieval")) %>% 
  select(participant, blockID, trialID, condition, screenID, 
         leftColor, rightColor, leftImage, leftSize, rightImage, rightSize, correctObject, correctJudge,
         response, acc, rt) %>% 
  rename(correctResp=correctJudge) %>% 
  mutate(response = as.character(response)) %>% 
  mutate(
    target = case_when(
      screenID=="memory-resp" & leftColor=="#FFFFFF" ~ rightImage,
      screenID=="memory-resp" & rightColor=="#FFFFFF" ~ leftImage,
      screenID=="retrieval" ~ correctObject,
      TRUE ~ NA_character_
    ),
    distractor = case_when(
      screenID=="memory-resp" & correctResp=="left" ~ leftImage,
      screenID=="memory-resp" & correctResp=="right" ~ rightImage,
      TRUE ~ NA_character_
    )
  ) %>% 
  mutate(
    distractor = case_when(
      screenID=="retrieval" ~ distractor[target==target][1],
      TRUE ~ distractor
    ),
    .by = c(participant, blockID, trialID)
  )

Data_Exp2b %>% write_csv(file = "./data/source/Data_Exp2b.csv")

Survey_Exp2b <- Raw_Exp2b %>% 
  filter(screenID == "survey") %>% 
  select(participant, response) %>% 
  unnest_wider(response) %>% 
  select(!starts_with("P0"))

Survey_Exp2b %>%
  write_csv(file = "./data/source/Survey_Exp2b.csv")

```


# Experiment 2c

## Download data
```{r}
# Download the data from JATOS
Metadata_Exp2c <- get_JATOS_data(
  token = "jap_bQ7jROzehBh7WTt0I2CrjLJyBZIUIfkd5079d",
  url = "https://coglab.xyz/jatos/api/v1/results",
  batchId = c(1518),
  dataPath = "./raw_data/Data_Exp2c/"
)

```

## Retrieve data
```{r}

Metadata_Exp2c <- read_metaData("./raw_data/Data_Exp2c/metadata.json") %>% 
  extract_data_info("participant")

Metadata_Exp2c_filtered <- Metadata_Exp2c %>% 
  filter(studyState == "FINISHED")

Raw_Exp2c <- read_json_data(Metadata_Exp2c_filtered$file) %>% 
  group_by(participant) %>% 
  mutate(participant = cur_group_id()) %>% 
  ungroup()

Data_Exp2c <- Raw_Exp2c %>%
  filter(blockID > 0, screenID %in% c("processing", "memory-resp", "retrieval")) %>% 
  select(participant, blockID, trialID, condition, screenID, 
         leftColor, rightColor, leftImage, leftSize, rightImage, rightSize, correctObject, correctJudge,
         response, acc, rt) %>% 
  rename(correctResp=correctJudge) %>% 
  mutate(response = as.character(response)) %>% 
  mutate(
    target = case_when(
      screenID=="memory-resp" & leftColor=="#FFFFFF" ~ rightImage,
      screenID=="memory-resp" & rightColor=="#FFFFFF" ~ leftImage,
      screenID=="retrieval" ~ correctObject,
      TRUE ~ NA_character_
    ),
    distractor = case_when(
      screenID=="memory-resp" & correctResp=="left" ~ leftImage,
      screenID=="memory-resp" & correctResp=="right" ~ rightImage,
      TRUE ~ NA_character_
    )
  ) %>% 
  mutate(
    distractor = case_when(
      screenID=="retrieval" ~ distractor[target==target][1],
      TRUE ~ distractor
    ),
    .by = c(participant, blockID, trialID)
  )

Data_Exp2c %>% write_csv(file = "./data/source/Data_Exp2c.csv")

Survey_Exp2c <- Raw_Exp2c %>% 
  filter(screenID == "survey") %>% 
  select(participant, response) %>% 
  unnest_wider(response) %>% 
  select(!starts_with("P0"))

Survey_Exp2c %>%
  write_csv(file = "./data/source/Survey_Exp2c.csv")

```

# Experiment 2d

## Download data
```{r}
# Download the data from JATOS
Metadata_Exp2d <- get_JATOS_data(
  token = "jap_bQ7jROzehBh7WTt0I2CrjLJyBZIUIfkd5079d",
  url = "https://coglab.xyz/jatos/api/v1/results",
  batchId = c(1539),
  dataPath = "./raw_data/Data_Exp2d/"
)

```

## Retrieve data
```{r}

Metadata_Exp2d <- read_metaData("./raw_data/Data_Exp2d/metadata.json") %>% 
  extract_data_info("participant")

Metadata_Exp2d_filtered <- Metadata_Exp2d %>% 
  filter(studyState == "FINISHED" | resultId %in% c("69779", "69801"))

Raw_Exp2d <- read_json_data(Metadata_Exp2d_filtered$file) %>% 
  group_by(participant) %>% 
  mutate(participant = cur_group_id()) %>% 
  ungroup()

Data_Exp2d <- Raw_Exp2d %>%
  filter(blockID > 0, screenID %in% c("processing", "memory-resp", "retrieval")) %>% 
  select(participant, blockID, trialID, condition, screenID, 
         leftColor, rightColor, leftImage, leftSize, rightImage, rightSize, correctObject, correctJudge,
         response, acc, rt) %>% 
  rename(correctResp=correctJudge) %>% 
  mutate(response = as.character(response)) %>% 
  mutate(
    target = case_when(
      screenID=="memory-resp" & leftColor=="#FFFFFF" ~ rightImage,
      screenID=="memory-resp" & rightColor=="#FFFFFF" ~ leftImage,
      screenID=="retrieval" ~ correctObject,
      TRUE ~ NA_character_
    ),
    distractor = case_when(
      screenID=="memory-resp" & correctResp=="left" ~ leftImage,
      screenID=="memory-resp" & correctResp=="right" ~ rightImage,
      TRUE ~ NA_character_
    )
  ) %>% 
  mutate(
    distractor = case_when(
      screenID=="retrieval" ~ distractor[target==target][1],
      TRUE ~ distractor
    ),
    .by = c(participant, blockID, trialID)
  )

Data_Exp2d %>% write_csv(file = "./data/source/Data_Exp2d.csv")

Survey_Exp2d <- Raw_Exp2d %>% 
  filter(screenID == "survey") %>% 
  select(participant, response) %>% 
  unnest_wider(response) %>% 
  select(!starts_with("P0"))

Survey_Exp2d %>%
  write_csv(file = "./data/source/Survey_Exp2d.csv")

```


# Experiment 3

## Download data
```{r}
# Download the data from JATOS
Metadata_Exp3a <- get_JATOS_data(
  token = "jap_bQ7jROzehBh7WTt0I2CrjLJyBZIUIfkd5079d",
  url = "https://coglab.xyz/jatos/api/v1/results",
  batchId = c(1553),
  dataPath = "./raw_data/Data_Exp3a/"
)

Metadata_Exp3b <- get_JATOS_data(
  token = "jap_bQ7jROzehBh7WTt0I2CrjLJyBZIUIfkd5079d",
  url = "https://coglab.xyz/jatos/api/v1/results",
  batchId = c(1551),
  dataPath = "./raw_data/Data_Exp3b/"
)

```

## Retrieve data
```{r}

Metadata_Exp3a <- read_metaData("./raw_data/Data_Exp3a/metadata.json") %>%
  filter(studyState == "FINISHED",!is.na(file)) %>% 
  extract_data_info("participant") %>% 
  mutate(group  = "groupC") %>% 
  slice(1:50)

Metadata_Exp3b <- read_metaData("./raw_data/Data_Exp3b/metadata.json") %>%
  filter(studyState == "FINISHED",!is.na(file)) %>%
  extract_data_info("participant") %>% 
  mutate(group = "groupD") %>% 
  slice(1:50)

Metadata_Exp3_filtered <- bind_rows(Metadata_Exp3a, Metadata_Exp3b)

Group_info <- Metadata_Exp3_filtered %>% 
  select(participant, group)

Raw_Exp3 <- read_json_data(Metadata_Exp3_filtered$file) %>% 
  left_join(Group_info) %>% 
  group_by(participant) %>% 
  mutate(participant = cur_group_id()) %>% 
  ungroup()

Data_Exp3 <- Raw_Exp3 %>%
  filter(blockID > 0, screenID %in% c("processing", "memory-resp", "retrieval")) %>% 
  select(participant, group, blockID, trialID, condition, screenID, 
         leftColor, rightColor, leftImage, leftSize, rightImage, rightSize, correctObject, correctJudge,
         response, acc, rt) %>% 
  rename(correctResp=correctJudge) %>% 
  mutate(response = as.character(response)) %>% 
  mutate(
    target = case_when(
      screenID=="memory-resp" & leftColor=="#FFFFFF" ~ rightImage,
      screenID=="memory-resp" & rightColor=="#FFFFFF" ~ leftImage,
      screenID=="retrieval" ~ correctObject,
      TRUE ~ NA_character_
    ),
    distractor = case_when(
      screenID=="memory-resp" & correctResp=="left" ~ leftImage,
      screenID=="memory-resp" & correctResp=="right" ~ rightImage,
      TRUE ~ NA_character_
    )
  ) %>% 
  mutate(
    distractor = case_when(
      screenID=="retrieval" ~ distractor[target==target][1],
      TRUE ~ distractor
    ),
    .by = c(participant, blockID, trialID)
  )

Data_Exp3 %>% write_csv(file = "./data/source/Data_Exp3.csv")

Survey_Exp3 <- Raw_Exp3 %>% 
  filter(screenID == "survey") %>% 
  select(participant, response) %>% 
  unnest_wider(response) %>% 
  select(!starts_with("P0"))

Survey_Exp3 %>%
  write_csv(file = "./data/source/Survey_Exp3.csv")

```


