---
title: "Processing Exp2"
author: "Chenyu Li"
format: html
editor: source
editor_options:
  chunk_output_type: console
---

# 1 Initial setting

## 1.1 Clear workspace and set default colors

```{r reset, include=FALSE}
# Clear all plots and variables from workspace
graphics.off()
rm(list=ls(all.names=TRUE))

# Set numerical precision and color schemes
options(digits = 3)
options(ggplot2.discrete.colour= c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A"))
options(ggplot2.discrete.fill= c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A"))
```

## 1.2 Import functions and packages

```{r}
# Install and load required packages
packages = c(
  # CRAN packages for data analysis and visualization
  "tidyverse", "brms", "ggpubr", "tidybayes", "emmeans", "bayestestR",
  # Github packages for specialized functions
  "chenyu-psy/smartr@v0.3.1",
  "chenyu-psy/taskr@v0.2.0",
  "venpopov/bmm"
)
process_packages(packages, quietly = TRUE)

# Source helper for readable condition labels in figures
source("./functions/factor_condition.R")

# Set default ggplot theme
theme_set(theme_bw())

# Define position dodge constants for plotting
dodge1 = position_dodge(.1)
dodge2 = position_dodge(.2)

# Define task name and directory paths
task <- "Exp1b"
model_path <- str_glue("./models/models_{task}/")
sample_path <- str_glue("./samples/sample_{task}/")
figure_path <- str_glue("./figures/figures_{task}/")


# Create directories if they don't exist
dir.create(file.path(model_path), showWarnings = FALSE)
dir.create(file.path(sample_path), showWarnings = FALSE)
dir.create(file.path(figure_path), showWarnings = FALSE)

# Run one background model-fitting task at a time so long Stan jobs are easy to monitor.
taskr::init_queue(max_slots = 1)

run_brm_task <- function(...) {
  brm(...)
  TRUE
}

```

# 2 Data processing

## 2.1 Import data

```{r}

Raw_data <- str_glue("./data/source/Data_{task}.csv") %>%
  read_csv() %>%
  mutate(condition = factor(condition, levels = c("A", "B","C","D")))

Survey_data <- str_glue("./data/source/Survey_{task}.csv") %>%
  read_csv()

```

## 2.2 Remove participants who were distracted or used aids during the experiments.

```{r}

excluding_aid_dist <- Survey_data %>%
  filter(str_detect(aid,"Yes") | str_detect(attention,"Yes")) %>%
  pull(participant)

message(str_glue("Excluded {length(excluding_aid_dist)} participants due to distraction or using aids."))

```

## 2.4 Remove participants whose accuracy for the size judgement task is lower than 50%.

```{r}

excluding_lowAcc <- Raw_data %>%
  filter(!participant %in% excluding_aid_dist) %>%
  filter(screenID == "memory-resp",condition!="A") %>%
  mutate(
    response = ifelse(response=="NULL", NA, response),
    acc = case_when(
      is.na(response) ~ NA,
      acc ~ 1,
      TRUE ~ 0)
    ) %>%
  summarise(
    pResp = sum(!is.na(response), na.rm = T)/n(),
    pAcc = mean(acc, na.rm = T),
    .by = c(participant)
  ) %>%
  filter((pResp < 0.5 | pAcc < 0.7)) %>%
  pull(participant)

message(str_glue("Excluded {length(excluding_lowAcc)} participants due to a low accuracy in the size judgement task"))

excluding_list <- c(excluding_aid_dist, excluding_lowAcc)
message(str_glue("Excluded {length(excluding_list)} participants in total"))

```

## 2.6 Formatting data

### 2.6.1 Size judgement task
```{r}

Data_Processing_Judge <- Raw_data %>%
  filter(screenID=="processing", !participant %in% excluding_list) %>%
  mutate(
    RT = rt/1000,
    phase = "processing",
    trialID = as.numeric(str_remove(trialID, "P"))
  ) %>%
  select(participant, blockID, trialID, condition, phase, correctResp, acc, RT)

Data_Memory_Judge <- Raw_data %>%
  filter(screenID=="memory-resp", !participant %in% excluding_list) %>%
  mutate(
    target = ifelse(leftImage=="image26", rightImage, leftImage),
    RT = rt/1000,
    phase = "memory",
    trialID = as.numeric(trialID)
  ) %>%
  select(participant, blockID, trialID, condition, phase, correctResp, target, acc, RT)

Data_Judge <- bind_rows(Data_Processing_Judge, Data_Memory_Judge) %>%
  arrange(participant, blockID, trialID, condition, phase, correctResp) %>%
  filter(condition!="A") %>%
  mutate(phase = factor(phase, levels = c("processing", "memory"), labels = c("Processing", "Memory + Processing"))) %>%
  mutate(
    RT = case_when(
      RT < 0.2 ~ NA,
      RT > mean(RT) + 3*sd(RT) ~ NA,
      RT < mean(RT) - 3*sd(RT) ~ NA,
      TRUE ~ RT
    )
  )

# Save the processed data
write_rds(Data_Judge, str_glue("./data/processed/Data_{task}_Judge.rds"))

```

### 2.6.2 Memory task

```{r}
Data_Ret <- Raw_data %>%
  filter(
    screenID == "retrieval",
    !participant %in% excluding_list
    ) %>%
  mutate(
    step = rank(trialID, ties.method = "first"),
    .by = c(participant, blockID, trialID)
  ) %>%
  select(participant, blockID, trialID, condition, step, target, distractor, response) %>%
  mutate(trialID = as.numeric(trialID)) %>%
  left_join(
    Data_Memory_Judge %>%
      select(participant, blockID, trialID, target, acc, RT) %>%
      rename(judge_acc = acc, judge_RT = RT)
  ) %>%
  mutate(
    Correct = ifelse(target==response, 1, 0),
    noRes = ifelse(response=="NULL", 1, 0)
  ) %>%
  mutate(
    Dist = ifelse(response==distractor, 1, 0),
    OtherDist = ifelse(Dist==0 & response %in% distractor, 1, 0),
    .by = c(participant, blockID, trialID, condition)
  ) %>%
  mutate(
    Other = ifelse(Correct==0 & response %in% target, 1, 0),
    NPL = 1 - Correct - Other - noRes,
    .by = c(participant, blockID, trialID, condition)
  ) %>%
  mutate(
    order = ifelse(condition == first(condition), 0, 1),
    .by = participant
  )

# Save the processed data
write_rds(Data_Ret, str_glue("./data/processed/Data_{task}_Ret.rds"))

```

### 2.6.3 Cognitive load data

```{r}

Data_Trial_Acc <- Data_Ret %>%
  summarise(
    acc = mean(Correct, na.rm = TRUE),
    correct = sum(Correct, na.rm = TRUE),
    nRet = sum(!is.na(Correct)),
    .by = c(participant, condition)
  )

Data_Trial_Load <- Data_Judge %>%
  filter(
    phase=="Processing",
    trialID > 15) %>%
  summarise(
    load = mean(RT, na.rm = TRUE)/2.5,
    .by = c(participant, condition)
  )

Data_Load <- Data_Trial_Acc %>%
  left_join(Data_Trial_Load, by = c("participant", "condition")) %>%
  filter(condition!="A",!is.na(load))

# Save the processed data
write_rds(Data_Load, str_glue("./data/processed/Data_{task}_load.rds"))
```


# 3 Data Visualization

## Plot RT across trial

```{r}

Plot_Judge_RT_trials <- Data_Judge %>%
  filter(acc==1) %>%
  agg_plot(y = RT, within = c(condition, phase, trialID), group = participant) %>%
  mutate(condition = factor_condition(condition)) %>%
  ggplot(aes(x = trialID, y = mean, color = phase, fill = phase)) +
  geom_smooth(method = "loess", se = TRUE)+
  facet_wrap(~ condition)+
  ylim(0,2)+
  labs(
    y = "Reaction time (s)",
    x = "Trial",
    color = "Phase",
    fill = "Phase")+
  theme(
    axis.text = element_text(size = 10.5),
    strip.text = element_text(size=10.5),
    strip.background = element_rect(fill = "#bababa"),
    axis.title = element_text(size = 10.5)
  )

ggsave(
  path = figure_path,
  filename = str_glue("Plot_{task}_RT_trials.png"),
  plot = Plot_Judge_RT_trials,
  width = 10,
  height = 4,
  dpi = 300,
  bg = "white")

```


## 3.1 Plot judgement task

```{r}

Plot_juadg_Acc <- Data_Judge %>%
  agg_plot(y = acc, within = c(condition, phase), group = participant) %>%
  mutate(condition = factor_condition(condition)) %>%
  ggplot(aes(x = condition, y = mean, fill = phase)) +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci), width = 0.1, position = dodge2)+
  geom_point(shape = 23, size = 3, position = dodge2)+
  ylim(0.5,1.03)+
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  labs(
    y = "Proportion of correct",
    x = "Condition", fill = "Trial type",
    title = "Accuracy",
    tag = "A")+
  theme(
    axis.text = element_text(size = 10.5)
  )


Plot_judge_RT <- Data_Judge %>%
  filter(acc==1) %>%
  agg_plot(y = RT, within = c(condition, phase), group = participant) %>%
  mutate(condition = factor_condition(condition)) %>%
  ggplot(aes(x = condition, y = mean, fill = phase)) +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci), width = 0.1, position = dodge2)+
  geom_point(shape = 23, size = 3, position = dodge2)+
  ylim(0.75,2)+
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  labs(
    y = "Reaction time (s)",
    x = "Condition",
    fill = "Trial type",
    title = "Reaction time",
    tag = "B")+
  theme(
    axis.text = element_text(size = 10.5)
  )

(Plot_juadgement <- ggarrange(
  Plot_juadg_Acc, Plot_judge_RT,
  common.legend = TRUE, legend = "right",
  ncol = 2, nrow = 1, widths = c(1, 1))
)

ggsave(
  path = figure_path,
  filename = str_glue("Plot_{task}_judgement.png"),
  plot = Plot_juadgement,
  width = 8,
  height = 4,
  dpi = 300,
  bg = "white")

```


## 3.2 Plot memory task

```{r}

Plot_Resp_correct <- Data_Ret %>%
  agg_plot(y = Correct, within = condition, group = participant) %>%
  mutate(condition = factor_condition(condition)) %>%
  ggplot(aes(x = condition, y = mean, fill=condition)) +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci), width = .1, position = dodge2)+
  geom_point(shape = 23, size = 3, position = dodge2)+
  ylim(0.3,0.8)+
  labs(
    y = "Proportion of response",
    x = "Condition")+
  scale_fill_manual(values = c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A")) +
  theme(
    legend.position = "none",
    axis.text = element_text(size = 10.5)
  )

ggsave(
  path = figure_path,
  filename = str_glue("Plot_{task}_response.png"),
  plot = Plot_Resp_correct,
  width = 3,
  height = 3.5,
  dpi = 300,
  bg = "white")

```

## Plot serial position curve on memory task
```{r}

Plot_Resp_correct_serialPos <- Data_Ret %>%
  agg_plot(y = Correct, within = c(condition, step), group = participant) %>%
  mutate(condition = factor_condition(condition)) %>%
  ggplot(aes(x = step, y = mean, color = condition, fill=condition)) +
  geom_line(linewidth=1, position = dodge2)+
  geom_errorbar(
    aes(ymin = mean-ci, ymax = mean+ci),
    linewidth = 0.8, width = .1, position = dodge2)+
  geom_point(shape = 23, size = 3, position = dodge2)+
  ylim(0.3,0.8)+
  labs(
    y = "Proportion of response",
    x = "Serial position",
    color = "Condition",
    fill = "Condition")+
  scale_color_manual(values = c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A")) +
  scale_fill_manual(values = c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A")) +
  theme(
    axis.text = element_text(size = 10.5),
    axis.title = element_text(size = 10.5)
  )

ggsave(
  path = figure_path,
  filename = str_glue("Plot_{task}_serialPosition.png"),
  plot = Plot_Resp_correct_serialPos,
  width = 6,
  height = 4,
  dpi = 300,
  bg = "white")

```

# 4 Model fitting

## 4.1 Size judgement task

### 4.1.1 Accuracy

#### data

```{r}
mData_judge_correct <- Data_Judge %>%
  summarise(
    score = sum(acc),
    nRet = n(),
    .by = c(participant, condition)
    ) %>%
  mutate(
    condition = factor(condition)
  )

contrasts(mData_judge_correct$condition) = bayestestR::contr.equalprior(n = 3)
```

#### Model fitting

```{r}
taskr::submit_task(
  fun = brms::brm,
  args = list(
    formula = score | trials(nRet) ~ 1 + condition + (1 + condition | participant),
    data = mData_judge_correct,
    family = binomial(),
    prior = c(prior(normal(0,1), class = "b"),
              prior(student_t(3, 0, 2), class = "sd", lb = 0)),
    chains = 8,
    iter = 10000,
    warmup = 2500,
    cores = 8,
    backend = "cmdstanr",
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    save_pars = save_pars(all = TRUE),
    file = str_glue("{model_path}Model_{task}_judge_Correct")
  ),
  label = str_glue("Model_{task}_judge_Correct"),
  output = "none"
)

```

#### Bayes Factor
```{r}

Model_judge_Correct <- readRDS(str_glue("{model_path}Model_{task}_judge_Correct.rds"))

taskr::submit_task(
  fun = unupdate,
  args = list(model = Model_judge_Correct),
  label = str_glue("Prior_{task}_judge_Correct"),
  output = "all"
)

Prior_judge_Correct <- taskr::get_task_result(str_glue("Prior_{task}_judge_Correct"))

bf_pairwise(
  Model_judge_Correct, Prior_judge_Correct,
  specs = c(~ condition))

```

      contrast |       BF
      -------------------
      B - C    | 2.08e+13
      B - D    | 1.44e+16
      C - D    |     8.19

### 4.1.3 Reaction time

#### Data

```{r}
mData_judge_RT <- Data_Judge %>%
  filter(acc==1) %>%
  mutate(condition = factor(condition))

contrasts(mData_judge_RT$condition) = bayestestR::contr.equalprior(n = 3)
```

#### Model fitting

```{r}
taskr::submit_task(
  fun = brms::brm,
  args = list(
    formula = RT ~ 1 + condition + (1 + condition | participant),
    data = mData_judge_RT,
    family = lognormal(),
    prior = c(prior(cauchy(0, sqrt(2)/4), class = "b"),
              prior(student_t(3, 0, 2), class = "sd", lb = 0)),
    chains = 8,
    iter = 10000,
    warmup = 2500,
    cores = 4,
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    save_pars = save_pars(all = TRUE),
    backend = "cmdstanr",
    file = str_glue("{model_path}Model_{task}_judge_RT")
  ),
  label = str_glue("Model_{task}_judge_RT"),
  output = "none"
)

```

#### Bayes Factor
```{r}

Model_judge_RT <- readRDS(str_glue("{model_path}Model_{task}_judge_RT.rds"))

taskr::submit_task(
  fun = unupdate,
  args = list(model = Model_judge_RT),
  label = str_glue("Prior_{task}_judge_RT"),
  output = "all"
)

Prior_judge_RT <- taskr::get_task_result(str_glue("Prior_{task}_judge_RT"))


# The processing effect
bf_pairwise(
  Model_judge_RT, Prior_judge_RT,
  specs = ~ condition)

```

      contrast |       BF
      -------------------
      B - C    | 6.98e+11
      B - D    | 3.70e+14
      C - D    | 1.59e+07

## 4.2 Memory task

### 4.2.1 Data

```{r}
mData_Ret <- Data_Ret %>%
  select(participant, condition, Correct) %>%
  summarise(
    Resp = sum(Correct, na.rm = TRUE),
    nResp = sum(!is.na(Correct)),
    .by = c(participant, condition)
  ) %>%
  mutate(
    simple = ifelse(condition!="A",1, 0),
    judge = ifelse(condition %in% c("C","D"), 1, 0),
    distractor = ifelse(condition=="D",1,0)
  )
```

```{r}
taskr::submit_task(
  fun = run_brm_task,
  args = list(
    data = mData_Ret,
    formula = Resp | trials(nResp) ~ 1 + simple + judge + distractor + (1 + simple + judge + distractor | participant),
    family = binomial(),
    prior = c(prior(normal(0,1), class = "b"),
              prior(student_t(3, 0, 2), class = "sd", lb = 0)),
    chains = 8,
    iter = 10000,
    warmup = 2500,
    cores = 4,
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    save_pars = save_pars(all = TRUE),
    sample_prior = "yes",
    backend = "cmdstanr",
    file = str_glue("{model_path}Model_{task}_memory_Correct")
    ),
  label = str_glue("Model_{task}_memory_Correct"),
  output = "none"
)
```

### Bayes Factor

```{r}
Model_memory_Correct <- readRDS(str_glue("{model_path}Model_{task}_memory_Correct.rds"))

bf_parameters(Model_memory_Correct)
```

      Parameter   |       BF
      ----------------------
      (Intercept) | 6.24e+03
      simple      |    0.139
      judge       |     1.00
      distractor  | 1.05e+04

