---
title: "Processing Exp 2c"
author: "Chenyu Li"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# 1 Initial setting

## 1.1 Clear workspace and set default colors

```{r reset, include=FALSE}
# Clear all plots and variables from workspace
graphics.off()
rm(list=ls(all.names=TRUE))

# Set numerical precision and color schemes
options(digits = 3)
options(ggplot2.discrete.colour= c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A"))
options(ggplot2.discrete.fill= c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A"))
```

## 1.2 Import functions and packages

```{r}
# Install and load required packages
packages = c(
  # CRAN packages for data analysis and visualization
  "tidyverse", "brms", "bmm", "ggpubr", "tidybayes", "emmeans", "bayestestR",
  # Github packages for specialized functions
  "chenyu-psy/smartr@v0.3.2"
)
process_packages(packages, quietly = TRUE)

# Source all local R functions from the functions directory
# load_functions("./functions")

# Set default ggplot theme
theme_set(theme_bw())

# Define position dodge constants for plotting
dodge1 = position_dodge(.1)
dodge2 = position_dodge(.2)

# Define task name and directory paths
task <- "Exp3"
model_path <- str_glue("./models/models_{task}/")
sample_path <- str_glue("./samples/sample_{task}/")
figure_path <- str_glue("./figures/figures_{task}/")

# Create directories if they don't exist
dir.create(file.path(model_path), showWarnings = FALSE)
dir.create(file.path(sample_path), showWarnings = FALSE)
dir.create(file.path(figure_path), showWarnings = FALSE)

```

# 2 Data processing

## 2.1 Import data

```{r}

Raw_data <- str_glue("./data/source/Data_{task}.csv") %>% 
  read_csv()

Survey_data <- str_glue("./data/source/Survey_{task}.csv") %>% 
  read_csv()

```

## 2.2 Remove participants who were distracted or used aids during the experiments.

```{r}

excluding_aid_dist <- Survey_data %>% 
  filter(str_detect(aid,"Yes") | str_detect(attention,"Yes")) %>% 
  pull(participant)

message(str_glue("Excluded {length(excluding_aid_dist)} participants due to distraction or using aids."))

```

## 2.3 Remove participants whose accuracy for the size judgement task is lower than 50%.

```{r}

excluding_lowAcc <- Raw_data %>% 
  filter(!participant %in% excluding_aid_dist) %>% 
  filter(screenID == "memory-resp",!str_detect(condition, "A|B")) %>% 
  mutate(
    response = ifelse(response=="NULL", NA, response),
    acc = case_when(
      is.na(response) ~ NA,
      acc ~ 1,
      TRUE ~ 0)
    ) %>% 
  summarise(
    pResp = sum(!is.na(response), na.rm = T)/n(),
    pAcc = mean(acc, na.rm = T),
    .by = c(participant)
  ) %>% 
  filter((pResp < 0.5 | pAcc < 0.65)) %>% 
  pull(participant)

message(str_glue("Excluded {length(excluding_lowAcc)} participants due to a low accuracy in the size judgement task"))

```

## 2.4 Formatting data

### 2.4.1 Judgement

```{r}
Data_Processing_Judge <- Raw_data %>% 
  filter(screenID=="processing", !participant %in% excluding_lowAcc) %>% 
  mutate(
    RT = rt/1000,
    phase = "processing",
    trialID = as.numeric(str_remove(trialID, "P")),
    ratio = leftSize/rightSize,
    ratio = ifelse(ratio > 1, 1/ratio, ratio)
  ) %>% 
  select(participant, group, blockID, trialID, condition, phase, ratio, correctResp, acc, RT)

Data_Memory_Judge <- Raw_data %>% 
  filter(screenID=="memory-resp", !participant %in% excluding_lowAcc) %>% 
  mutate(
    target = ifelse(leftImage=="image26", rightImage, leftImage),
    RT = rt/1000,
    phase = "memory",
    trialID = as.numeric(trialID),
    ratio = leftSize/rightSize,
    ratio = ifelse(ratio > 1, 1/ratio, ratio)
  ) %>%
  select(participant, group, blockID, trialID, condition, phase, ratio, correctResp, target, acc, RT)

Data_Judge <- bind_rows(Data_Processing_Judge, Data_Memory_Judge) %>% 
  arrange(participant, group, blockID, trialID, condition, phase, correctResp) %>% 
  filter(condition!="A") %>% 
  mutate(phase = factor(phase, levels = c("processing", "memory"), labels = c("Processing", "Memory + Processing"))) %>% 
  mutate(
    RT = case_when(
      RT < 0.2 ~ NA,
      RT > mean(RT) + 3*sd(RT) ~ NA,
      RT < mean(RT) - 3*sd(RT) ~ NA,
      TRUE ~ RT
    )
  )

# Save the processed data
write_rds(Data_Judge, str_glue("./data/processed/Data_{task}_Judge.rds"))
```

### 2.4.2 Retrieval
```{r}

Data_Ret <- Raw_data %>% 
  filter(
    screenID == "retrieval", 
    !participant %in% excluding_lowAcc
    ) %>% 
  mutate(
    step = rank(trialID, ties.method = "first"),
    .by = c(participant, blockID, trialID)
  ) %>% 
  select(participant, group, blockID, trialID, condition, step, target, distractor, response) %>% 
  mutate(trialID = as.numeric(trialID)) %>%
  left_join(
    Data_Memory_Judge %>% 
      select(participant, blockID, trialID, target, acc, RT) %>% 
      rename(judge_acc = acc, judge_RT = RT)
  ) %>% 
  mutate(
    Correct = ifelse(target==response, 1, 0),
    noRes = ifelse(response=="NULL", 1, 0)
  ) %>% 
  mutate(
    Dist = ifelse(response==distractor, 1, 0),
    OtherDist = ifelse(Dist==0 & response %in% distractor, 1, 0),
    .by = c(participant, blockID, trialID, condition)
  ) %>% 
  mutate(
    Other = ifelse(Correct==0 & response %in% target, 1, 0),
    NPL = 1 - Correct - Other - noRes,
    .by = c(participant, blockID, trialID, condition)
  ) %>% 
  mutate(
    order = ifelse(condition == first(condition), 0, 1),
    .by = participant
  )

# Save the processed data
write_rds(Data_Ret, str_glue("./data/processed/Data_{task}_Ret.rds"))

```

### 2.4.3 Cognitive load

```{r}

Data_Trial_Acc <- Data_Ret %>% 
  summarise(
    acc = mean(Correct, na.rm = TRUE),
    correct = sum(Correct, na.rm = TRUE),
    nRet = sum(!is.na(Correct)),
    .by = c(participant, group, condition)
  )

Data_Trial_Load <- Data_Judge %>% 
  filter(
    phase=="Processing", 
    trialID > 15,
    ) %>%
  summarise(
    load = mean(RT, na.rm = TRUE)/3,
    .by = c(participant, group, condition)
  )

Data_Load <- Data_Trial_Acc %>% 
  left_join(Data_Trial_Load, by = c("participant", "group", "condition")) %>% 
  filter(!is.na(load))

# Save the processed data
write_rds(Data_Load, str_glue("./data/processed/Data_{task}_load.rds"))

```

# 3 Data Visualization

## 3.1 Plot RT across trial

### Data

```{r}

pData_Judge_RT_trials <- Data_Judge %>% 
  filter(acc==1) %>%
  mutate(
    trialID = case_when(
      phase == "Processing" ~ trialID,
      phase == "Memory + Processing" ~ trialID + 25
    )
  )



```

### Plot the B condition between group C and D

```{r}

Plot_Judge_RT_trials_B <- pData_Judge_RT_trials %>% 
  filter(condition == "B") %>%
  mutate(group = factor(
    group, 
    levels = c("groupC", "groupD"),
    labels = c("C group", "D group"))
  ) %>%
  agg_plot(y = RT, between = group, within = c(condition, phase, trialID), group = participant) %>%
  ggplot(aes(x = trialID, y = mean, color = phase, fill = phase, linetype = group)) +
  geom_smooth(method = "loess", se = TRUE)+
  facet_wrap(~ condition, nrow = 2, labeller = labeller(condition = ~paste0("Condition ", .)))+
  ylim(0,2.5)+
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_linetype_manual(
    values = c("solid", "dashed"), # Or any linetypes you want for C group and D group
    guide = guide_legend(override.aes = list(color = "black"))
  ) +
  labs(
    y = "Reaction time (s)", 
    x = "Trial",
    linetype = "Group")+
  guides(fill = "none", color = "none") +
  theme(
    legend.position = "inside",
    legend.justification = c(1,0),
    legend.position.inside = c(0.98, 0.02),
    legend.key.width = unit(1.5, "cm"),
    axis.text = element_text(size = 10.5),
    strip.text = element_text(size=10.5),
    strip.background = element_rect(fill = "#bababa"),
    axis.title = element_text(size = 10.5)
  )



```

### Plot the C and D condition

```{r}

Plot_Judge_RT_trials_CD <- pData_Judge_RT_trials %>% 
  filter(condition %in% c("C1", "C2", "D1", "D2")) %>%
  mutate(
    judgement = ifelse(str_detect(condition, "1"), "Regular", "Doubled"),
    judgement = factor(judgement, levels = c("Regular", "Doubled")),
    condition = ifelse(str_detect(condition, "C"), "C", "D")
  ) %>%
  agg_plot(y = RT, within = c(judgement, condition, phase, trialID), group = participant) %>%
  ggplot(aes(x = trialID, y = mean, color = phase, fill = phase, linetype = judgement)) +
  geom_smooth(method = "loess", se = TRUE)+
  facet_wrap(~ condition, labeller = labeller(condition = ~paste0("Condition ", .)))+
  ylim(0,2.5)+
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_linetype_manual(
    values = c("solid", "dashed"), 
    guide = guide_legend(override.aes = list(color = "black"))
  ) +
  labs(
    y = "Reaction time (s)", 
    x = "Trial",
    linetype = "Judgement task")+
  guides(fill = "none", color = "none") +
  theme(
    legend.position = "inside",
    legend.justification = c(1,0),
    legend.position.inside = c(0.98, 0.02),
    legend.key.width = unit(1.5, "cm"),
    axis.text = element_text(size = 10.5),
    strip.text = element_text(size=10.5),
    strip.background = element_rect(fill = "#bababa"),
    axis.title = element_text(size = 10.5)
  )



```


### Combine plots
```{r}

Plot_for_legend <- pData_Judge_RT_trials %>% 
  filter(condition == "B") %>%
  agg_plot(y = RT, within = c(condition, phase, trialID), group = participant) %>%
  ggplot(aes(x = trialID, y = mean, color = phase, fill = phase)) +
  geom_smooth(method = "loess", se = TRUE)+
  facet_wrap(~ condition, nrow = 2, labeller = labeller(condition = ~paste0("Condition ", .)))+
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  labs(
    color = "Phase",
    fill = "Phase"
  )

(Plot_Judge_RT_trials <- ggarrange(
  Plot_Judge_RT_trials_B, Plot_Judge_RT_trials_CD,
  common.legend = FALSE,
  ncol = 2, nrow = 1, widths = c(1.1, 2.1)) %>% 
  annotate_figure(
    right = get_legend(Plot_for_legend))
)

ggsave(
  filename = str_glue("{figure_path}Plot_{task}_RT_trials.pdf"),
  plot = Plot_Judge_RT_trials,
  bg = "white",
  width = 10, height = 4)
```


## 3.2 Plot judgement task

```{r}

Plot_juadg_Acc <- Data_Judge %>% 
  agg_plot(y = acc, between = group, within = c(condition, phase), group = participant) %>%
  mutate(group = factor(
    group, 
    levels = c("groupC", "groupD"),
    labels = c("C group", "D group"))
  ) %>%
  ggplot(aes(x = condition, y = mean, fill = phase)) +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci), linewidth = 0.7, width = 0.15, position = dodge2)+
  geom_point(shape = 23, size = 3, position = dodge2)+
  ylim(0.5,1.03)+
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  facet_grid(~ group, scales = "free_x") +
  labs(
    y = "Proportion of correct", 
    x = "Condition", fill = "Trial type",
    title = "Accuracy",
    tag = "A")+
  theme(
    strip.text = element_text(size=10.5),
    strip.background = element_rect(fill = "#bababa"),
    axis.text = element_text(size = 10.5),
    axis.title = element_text(size = 10.5)
  )


Plot_judge_RT <- Data_Judge %>% 
  filter(acc==1) %>%
  agg_plot(y = RT, between = group, within = c(condition, phase), group = participant) %>% 
  mutate(group = factor(
    group, 
    levels = c("groupC", "groupD"),
    labels = c("C group", "D group"))
  ) %>%
  ggplot(aes(x = condition, y = mean, fill = phase)) +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci), linewidth = 0.7, width = 0.15, position = dodge2)+
  geom_point(shape = 23, size = 3, position = dodge2)+
  ylim(0.5,2.2)+
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  facet_grid(~ group, scales = "free_x") +
  labs(
    y = "Reaction time (s)", 
    x = "Condition", 
    fill = "Trial type",
    title = "Reaction time",
    tag = "B")+
  theme(
    strip.text = element_text(size=10.5),
    strip.background = element_rect(fill = "#bababa"),
    axis.text = element_text(size = 10.5),
    axis.title = element_text(size = 10.5)
  )

(Plot_juadgement <- ggarrange(
  Plot_juadg_Acc, Plot_judge_RT,
  common.legend = TRUE, legend = "right",
  ncol = 2, nrow = 1, widths = c(1, 1))
)

ggsave(
  filename = str_glue("{figure_path}Plot_{task}_judgement.pdf"),
  plot = Plot_juadgement,
  bg = "white",
  width = 10, height = 4)

```


## 3.3 Plot memory task

```{r}

Plot_Resp_correct <- Data_Ret %>% 
  agg_plot(y = Correct, between = group, within = condition, group = participant) %>%
  mutate(group = factor(
    group, 
    levels = c("groupC", "groupD"),
    labels = c("C group", "D group"))
  ) %>%
  ggplot(aes(x = condition, y = mean, fill=condition)) +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci), linewidth = 0.7, width = .05, position = dodge2)+
  geom_point(shape = 23, size = 3, position = dodge2)+
  facet_grid(~ group, scales = "free_x") +
  ylim(0.4,0.8)+
  labs(
    y = "Proportion of response", 
    x = "Condition")+
  scale_fill_manual(values = c("B"="#FF7F6F","C1"="#2F7FC1", "C2"="#21597B","D1"="#FFBE7A","D2"="#FF7F00")) +
  theme(
    legend.position = "none",
    strip.text = element_text(size=10.5),
    strip.background = element_rect(fill = "#bababa"),
    axis.text = element_text(size = 10.5),
    axis.title = element_text(size = 10.5)
  )

ggsave(
  filename = str_glue("{figure_path}Plot_{task}_response.pdf"),
  plot = Plot_Resp_correct,
  bg = "white",
  width = 6, height = 4.5)


```

## 3.5 Plot cognitive load

```{r}
Data_Load_acc <- Data_Load %>% 
  agg_plot(y = acc, between = group, within = c(condition), group = participant) %>% 
  select(group, condition, mean, ci) %>% 
  rename(acc = mean, acc_ci = ci)

Data_Load_load <- Data_Load %>% 
  agg_plot(y = load, between = group, within = c(condition), group = participant) %>% 
  select(group, condition, mean, ci) %>% 
  rename(load = mean, load_ci = ci)

Plot_cognitive_load <- left_join(Data_Load_acc, Data_Load_load) %>% 
  mutate(group = factor(
    group, 
    levels = c("groupC", "groupD"),
    labels = c("C group", "D group"))
  ) %>%
  ggplot(aes(x = load, y = acc, group = 1, color = condition)) +
  geom_line(color = "grey", linewidth=1) +
  geom_errorbar(
    aes(ymin = acc - acc_ci, ymax = acc + acc_ci),
    linewidth = 0.8, width = 0) +
  geom_errorbar(
    aes(xmin = load - load_ci, xmax = load + load_ci),
    linewidth = 0.8,  orientation = "y", width = 0) +
  geom_point(size = 2.5) +
  facet_grid(~ group, scales = "free_x") +
  labs(
    x = "Cognitive load", 
    y = "Proportion of correct",
    color = "Condition") +
  ylim(0.4, 0.8) +
  scale_color_manual(values = c("B"="#FF7F6F","C1"="#2F7FC1", "C2"="#21597B","D1"="#FFBE7A","D2"="#FF7F00")) +
  theme(
    strip.text = element_text(size=10.5),
    strip.background = element_rect(fill = "#bababa"),
    axis.text = element_text(size = 10.5),
    axis.title = element_text(size = 10.5)
  )

ggsave(
  filename = str_glue("{figure_path}Plot_{task}_cognitiveLoad.pdf"),
  plot = Plot_cognitive_load,
  bg = "white",
  width = 6, height = 4)

```


## 3.6 Plot the relationship between size similarity and RT

```{r}

Plot_similarity_RT <- Data_Judge %>% 
  filter(!condition %in% c("A", "B")) %>% 
  select(participant, condition, phase, ratio, RT) %>% 
  ggplot(aes(x = ratio, y = RT, group = phase, color = phase, fill = phase)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = TRUE) +
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  labs(
    x = "Ratio",
    y = "Reaction time (s)",
    fill = "Trial type",
    color = "Trial type"
  )


Plot_similarity_acc <- Data_Judge %>% 
  filter(!condition %in% c("A", "B")) %>% 
  select(participant, condition, phase, ratio, acc) %>% 
  mutate(bin = cut_interval(ratio, n = 5)) %>%
  summarise(
    acc = mean(acc, na.rm = TRUE),
    .by = c(participant, phase, bin)
  ) %>% 
  ggplot(aes(x = as.numeric(bin), y = acc, group = phase, color = phase, fill = phase)) +
  geom_jitter(width = 0.1, alpha = 0.5) +
  geom_smooth(method = "loess", se = TRUE) +
  scale_color_manual(values = c("#FFBE7A","#8FC0A9")) +
  scale_fill_manual(values = c("#FFBE7A","#8FC0A9")) +
  coord_cartesian(ylim = c(0,1)) +
  scale_x_continuous(
    breaks = 1:5, 
    labels = c("0 - 0.2", "0.2 - 0.4", "0.4 - 0.6", "0.6 - 0.8", "0.8 - 1.0") 
  ) +
  labs(
    x = "Ratio",
    y = "Accuracy",
    fill = "Trial type",
    color = "Trial type"
  )

(Plot_similarity <- ggarrange(
  Plot_similarity_acc, Plot_similarity_RT,
  common.legend = TRUE, legend = "right",
  ncol = 2, nrow = 1, widths = c(1, 1)
))

ggsave(
  plot = Plot_similarity,
  path = figure_path,
  filename = str_glue("Plot_{task}_similarity.pdf"),
  bg = "white",
  width = 10, height = 4
)


```



# 4 Model fitting

## 4.1 Size judgement task

### 4.1.1 Accuracy

#### 4.1.1.1 Model fitting

```{r}

mData_judge_correct <- Data_Judge %>% 
  summarise(
    score = sum(acc),
    nRet = n(),
    .by = c(participant, condition)
    ) %>% 
  mutate(
    condition = factor(condition)
  )

contrasts(mData_judge_correct$condition) = bayestestR::contr.equalprior(n = 2)


smart_runFun(
  fun = brm,
  args = list(
    formula = score | trials(nRet) ~ 1 + condition + (1 + condition | participant),
    data = mData_judge_correct,
    family = binomial(),
    prior = c(prior(normal(0,1), class = "b"), 
              prior(student_t(3, 0, 2), class = "sd", lb = 0)),
    chains = 8,
    iter = 10000,
    warmup = 2500,
    cores = 8,
    backend = "cmdstanr",
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    save_pars = save_pars(all = TRUE),
    file = str_glue("{model_path}Model_{task}_judge_Correct")
  ),
  name = str_glue("Model_{task}_judge_Correct"),
)


```

#### 4.1.1.2 Bayes Factor
```{r}

Model_judge_Correct <- readRDS(str_glue("{model_path}Model_{task}_judge_Correct.rds"))

smart_runFun(
  fun = unupdate,
  args = list(model = Model_judge_Correct),
  name = str_glue("Prior_{task}_judge_Correct"),
  export = "Prior_judge_Correct"
)

# The set-size effect
bf_pairwise(
  Model_judge_Correct, Prior_judge_Correct, 
  specs = c(~ condition))

# contrast         |       BF
# ---------------------------
# complex - simple | 5.18e+07

```



### 4.1.2 Reaction time

#### 4.1.2.1 Model fitting

```{r}
mData_judge_RT <- Data_Judge %>% 
  filter(acc==1) %>% 
  mutate(condition = factor(condition))

contrasts(mData_judge_RT$condition) = bayestestR::contr.equalprior(n = 2)

smart_runFun(
  fun = brm,
  args = list(
    formula = RT ~ 1 + condition + (1 + condition | participant),
    data = mData_judge_RT,
    family = lognormal(),
    prior = c(prior(cauchy(0, sqrt(2)/4), class = "b"), 
              prior(student_t(3, 0, 2), class = "sd", lb = 0)),
    chains = 8,
    iter = 10000,
    warmup = 2500,
    cores = 8,
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    save_pars = save_pars(all = TRUE),
    backend = "cmdstanr",
    file = str_glue("{model_path}Model_{task}_judge_RT")
  ),
  name = str_glue("Model_{task}_judge_RT"),
)
```

#### 4.1.2.2 Bayes Factor
```{r}

Model_judge_RT <- readRDS(str_glue("{model_path}Model_{task}_judge_RT.rds"))

smart_runFun(
  fun = unupdate,
  args = list(model = Model_judge_RT),
  name = str_glue("Prior_{task}_judge_RT"),
  export = "Prior_judge_RT"
)


# The processing effect
bf_pairwise(
  Model_judge_RT, Prior_judge_RT, 
  specs = ~ condition)

# contrast         |    BF
# ------------------------
# complex - simple | 86.02

```


## 4.2 Memory task

### 4.2.1 Data

```{r}

mData_Ret <- Data_Ret %>% 
  select(participant, group, condition, Correct) %>% 
  summarise(
    Resp = sum(Correct, na.rm = TRUE),
    nResp = sum(!is.na(Correct)),
    .by = c(participant, group, condition)
  ) %>% 
  mutate(
    judge = ifelse(!condition == "B", 1, 0),
    load = ifelse(str_detect(condition, "2"), 1, 0),
    distractor = ifelse(str_detect(condition, "D"),1,0)
  )

smart_runFun(
  fun = brm,
  args = list(
    data = mData_Ret,
    formula = Resp | trials(nResp) ~ 1 + judge + load + distractor + (1 + judge + load | gr(participant, by = group)),
    family = binomial(),
    prior = c(prior(normal(0,1), class = "b"), 
              prior(student_t(3, 0, 2), class = "sd", lb = 0)),
    chains = 8,
    iter = 10000,
    warmup = 2500,
    cores = 8,
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    save_pars = save_pars(all = TRUE),
    sample_prior = "yes",
    backend = "cmdstanr",
    file = str_glue("{model_path}Model_{task}_memory_Correct")),
  name = str_glue("Model_{task}_memory_Correct"),
)


Model_memory_Correct <- readRDS(str_glue("{model_path}Model_{task}_memory_Correct.rds"))

bf_parameters(Model_memory_Correct)

"
Parameter   |       BF
----------------------
(Intercept) | 3.03e+04
judge       |    0.096
load        |    0.153
distractor  |   217.89
"

```





